### 2022-03-21 src/text/6-acknowledgements.tex
Reformat tex files

TODO: copy over stuff from \url{http://docs.gammapy.org/en/latest/about.html#thanks}.
TODO: add the ANR for Luca (and Atreyee in LUPM?)

>>>>

	TODO: copy over stuff from
	\url{http://docs.gammapy.org/en/latest/about.html#thanks}.

	TODO: add the ANR for Luca (and Atreyee in LUPM?)

	J.E. Ruiz acknowledges financial support from the State Agency for Research of the Spanish MCIU through the "Center of Excellence Severo Ochoa" award to the Instituto de Astrof\'isica de Andaluc\'ia (SEV-2017-0709)
